Assessing exposure to Atlantic Basin tropical storms in United States counties

### 2016-09-08 writing/DraftExposurePaper/DraftExposurePaper.Rmd
Update now that `rnoaa` is on CRAN

```{r echo = FALSE, message = FALSE, warning = FALSE}
library(hurricaneexposuredata)
library(hurricaneexposure)
library(knitr)
library(ggplot2)
library(ggthemes)
library(grid)
library(gridExtra)
library(plyr)
library(dplyr)
library(tidyr)
library(choroplethr)
library(RColorBrewer)
library(weathermetrics)
library(lubridate)
library(xtable)

#devtools::install_github("ropenscilabs/rnoaa")
library(rnoaa)
#devtools::install_github("leighseverson/countyweather")
options("noaakey" = Sys.getenv("noaakey"))
library(countyweather)

@@

        ex_weather <- readRDS(paste0(ex_dir, ex_fips, ".rds"))
        ex_weather <- as.data.frame(ex_weather$averaged)

@@

        ex_rain <- county_rain(counties = ex_fips,
                               start_year = 1988, end_year = 2011,
                               rain_limit = 0, dist_limit = 2000) %>%
                full_join(ex_weather, by = "storm_id") %>%
                filter(!is.na(prcp) & !is.na(tot_precip))

@@

i <- plot_county_rain_compare(ex_fips = "01097", ex_dir = "mobile_data/",
                         ex_title = "Mobile County, AL", get_data = TRUE)

>>>>

```{r echo = FALSE, message = FALSE, warning = FALSE}
library(hurricaneexposuredata)
library(hurricaneexposure)
library(knitr)
library(ggplot2)
library(ggthemes)
library(grid)
library(gridExtra)
library(plyr)
library(dplyr)
library(tidyr)
library(choroplethr)
library(RColorBrewer)
library(weathermetrics)
library(lubridate)
library(xtable)
library(rnoaa)

#devtools::install_github("leighseverson/countyweather")
options("noaakey" = Sys.getenv("noaakey"))
library(countyweather)

@@

        ex_weather <- readRDS(paste0(ex_dir, ex_fips, ".rds"))
        ex_weather <- as.data.frame(ex_weather$daily_weather)

@@

        ex_rain <- county_rain(counties = ex_fips,
                               start_year = 1988, end_year = 2011,
                               rain_limit = 0, dist_limit = 500) %>%
                full_join(ex_weather, by = "storm_id") %>%
                filter(!is.na(prcp) & !is.na(tot_precip))

        ave_n <- round(mean(ex_rain$ave_n, na.rm = TRUE))
        n_storms <- nrow(ex_rain)
        ex_title <- paste0(ex_title, "\n(", n_storms, "; ", ave_n, ")")

@@

i <- plot_county_rain_compare(ex_fips = "01097", ex_dir = "mobile_data/",
                         ex_title = "Mobile County, AL")
